MCTS Based on Simple Regret

### 2012-02-22 slides/slides.tex
max->min
done/todo

{\bf S}imple {\bf R}egret followed by {\bf C}umulative {\bf R}egret.
\begin{itemize}
\item Maximizes {\bf simple regret} at the {\bf first step}.
\item Continues with UCT from the {\bf second step on}.
\end{itemize}
\vspace{1em}
\begin{algorithmic}[1]
\Procedure{Rollout}{node, depth=1}
  \If {\Call{IsLeaf}{node, depth}}
    \State \textbf{return} 0
  \Else
    \State \textbf{if} depth=1 \textbf{then} action $\gets$ \Call{FirstAction}{node} \label{alg:srcr-first-action}   
    \State \textbf{else} action $\gets$ \Call{NextAction}{node} \label{alg:srcr-next-action}
    \State next-node $\gets$ \Call{NextState}{node, action}
    \State reward $\gets$ \Call{Reward}{node, action, next-node}
     \State \hspace{4em} + \Call{Rollout}{next-node, depth+1}
    \State \Call{UpdateStats}{node, action, reward}
  \EndIf
\EndProcedure
\end{algorithmic}
\end{frame}

@@

\onslide<+->
$\varepsilon$-greedy:
\begin{itemize} 
\item Pulls the empirically best arm with probability $\varepsilon$.
\item Any other arm with probability $\frac {1-epsilon} {K-1}$.
\item Exhibits exponentially decreasing simple regret.
\item Uniform sampling when $\varepsilon=\frac 1 K$, much better when
  $\varepsilon=\frac 1 2$.
\end{itemize}
\vspace{1em}
\onslide<+->
$UCB_{\sqrt{\cdot}}$ ($\sqrt{\cdot}$ instead of $\log$): 
\begin{itemize}
\item Pulls arm $i$ that maximizes
  $b_i=\overline X_i+\sqrt {\frac {c \sqrt n} {n_i}}$. 
\item Exhibits superpolynomially decreasing simple regret.
\end{itemize}
\end{frame}

@@

\begin{frame}{Summary}
\begin{itemize}
\item<+-> Improved MCTS scheme, SRCR, introduced.
\item<+-> SRCR performs better than unmodified UCT.
\item<+-> VOI-aware sampling for minimizing sampling regret proposed.
\item<+-> Better sampling schemes can be developed based on principles
  of Rational Metareasoning.
\item<+-> UCT is not well understood. Better understanding will help
  in developing efficient  MCTS schemes and adapting to different domains.
\end{itemize}
\end{frame}

>>>>

{\bf S}imple {\bf R}egret followed by {\bf C}umulative {\bf R}egret.
\begin{itemize}
\item Minimizes {\bf simple regret} at the {\bf first step}.
\item Continues with UCT from the {\bf second step on}.
\end{itemize}
\vspace{1em}
\begin{algorithmic}[1]
\Procedure{Rollout}{node, depth=1}
  \If {\Call{IsLeaf}{node, depth}}
    \State \textbf{return} 0
  \Else
    \State \textbf{if} depth=1 \textbf{then} action $\gets$ \Call{FirstAction}{node} \label{alg:srcr-first-action}   
    \State \textbf{else} action $\gets$ \Call{NextAction}{node} \label{alg:srcr-next-action}
    \State next-node $\gets$ \Call{NextState}{node, action}
    \State reward $\gets$ \Call{Reward}{node, action, next-node}
     \State \hspace{4em} + \Call{Rollout}{next-node, depth+1}
    \State \Call{UpdateStats}{node, action, reward}
  \EndIf
\EndProcedure
\end{algorithmic}
\end{frame}

@@

\onslide<+->
$\varepsilon$-greedy:
\begin{itemize} 
\item Pulls the empirically best arm with probability $\varepsilon$.
\item Any other arm with probability $\frac {1-\varepsilon} {K-1}$.
\item Exhibits exponentially decreasing simple regret.
\item Uniform sampling when $\varepsilon=\frac 1 K$, much better when
  $\varepsilon=\frac 1 2$.
\end{itemize}
\vspace{1em}
\onslide<+->
$UCB_{\sqrt{\cdot}}$ ($\sqrt{\cdot}$ instead of $\log$): 
\begin{itemize}
\item Pulls arm $i$ that maximizes
  $b_i=\overline X_i+\sqrt {\frac {c \sqrt n} {n_i}}$. 
\item Exhibits superpolynomially decreasing simple regret.
\end{itemize}
\end{frame}

@@

\begin{frame}{Summary}
\onslide<+->
Done:
\begin{itemize}
\item Improved MCTS scheme, SRCR, introduced.
\item SRCR performs better than unmodified UCT.
\item VOI-aware sampling for minimizing sampling regret proposed.
\end{itemize}
\onslide<+->
TODO:
\begin{itemize}
\item Better sampling schemes can be developed based on principles
  of Rational Metareasoning.
\item UCT is not well understood. Better understanding will help
  in developing efficient  MCTS schemes and adapting to different domains.
\end{itemize}
\end{frame}
